---
title: "Attrition Models"
author: "Adam Canton"
date: "8/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ROCR)
library(magrittr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(naniar)
library(GGally)
library(e1071)
library(class)
library(caret)
library(MASS)
library(caret)
library(ggcorrplot)
library(Lahman)
library(olsrr)
library(glmnet)
```

```{r}
# Get data
cs2.data <- read.csv(file = "F:/R For Real/DDS-Case-Study-2/CaseStudy2-data.csv", sep = ",", header = TRUE)


# data excluded as it is constant
exclude_factors = c("EmployeeCount",'Over18','StandardHours')
cs2.data = cs2.data %>% dplyr::select(-all_of(exclude_factors))

# Creates a numeric analog to for models that have continous inputs only 
cs2.data <- cs2.data %>% mutate(AttNum = ifelse(Attrition == "No",0,1))

# creates a data set of numeric Values
cs2.numeric = cs2.data %>% dplyr::select(Age, DailyRate, DistanceFromHome, HourlyRate, MonthlyIncome, MonthlyRate, NumCompaniesWorked, PercentSalaryHike,
                                  TotalWorkingYears, TrainingTimesLastYear, YearsAtCompany, YearsInCurrentRole, YearsSinceLastPromotion,
                                  YearsWithCurrManager,AttNum)

# cs2.reduced - model for finding interactions
cs2.Reduced <-  cs2.data %>% dplyr::select(JobLevel, Education, JobRole, MaritalStatus, TotalWorkingYears, DistanceFromHome, Attrition)
```


# Set sample
## Watch out for what data set you are sampling
```{r}
# Create Log Regression with Normal Variables Train and Test sets ----
# If we are looking for interactions through the step function - sample the reduced model - If doing reduced Comment out the exclude factors and following selects
# Forcing a 50/50 sample  - these leaves the test set as 630 No's and 40 Yes's or a 94/6 test split

cs2.yes <- subset(cs2.data, Attrition == "Yes")
cs2.no <- subset(cs2.data, Attrition == "No")

DimYes <- 100
DimNo <- 100

set.seed(35)
index.yes <- sample(1:dim(cs2.yes)[1],DimYes,replace=F)
train.yes <- cs2.yes[index.yes,]
test.yes <- cs2.yes[-index.yes,]

index.no <- sample(1:dim(cs2.no)[1],DimNo,replace=F)
train.no <- cs2.no[index.no,]
test.no <- cs2.no[-index.no,]

cs2.LogTrain <- rbind(train.no, train.yes)
cs2.LogTest <- rbind(test.no, test.yes)

exclude_factors <- c("ID", "AttNum")

cs2.LogTrain <- cs2.LogTrain %>% dplyr::select(-all_of(exclude_factors))
cs2.LogTest <- cs2.LogTest %>% dplyr::select(-all_of(exclude_factors))

# remove intermediate data sets
rm(test.no, test.yes, train.no, train.yes, cs2.no, cs2.yes)

```


# Step Model 
## Also used to find significant interactions when using the reduced data set
```{r, warning = FALSE}
# Creates Step Model from Full - 
# if looking for significant interactions from the reduced model change Attrition ~ . to Attrition ~ (.)^2
# Did not find any significant interactions from the reduced model

full.log <- glm(Attrition ~ (.)^2, family = 'binomial', data = cs2.LogTrain)
step.log <- full.log %>% stepAIC(trace = FALSE)


summary(step.log) 

# Get predictions from Step Model
fit.pred.step <- predict(step.log, newdata = cs2.LogTest, type = "response")

p = data.frame(Att = cs2.LogTest$Attrition, Preds = fit.pred.step)
names(p)[2] <- 'Preds'
p %>% group_by(Att, Preds) %>% ggplot(aes(x = Preds, fill = Att)) + geom_boxplot() + facet_grid(rows = vars(p$Att))

cutoff.step = 0.41

class.step <- factor(ifelse(fit.pred.step > cutoff.step, "Yes", "No"), levels = c("No", "Yes"))

print("Confusion Step")
confusionMatrix(class.step, cs2.LogTest$Attrition)
```
# Lasso Model
# Selects minimum lambda value
```{r}
# Build Lasso Model on train set, finds optimal Lambda
cs2.Train.x <- model.matrix(Attrition ~ ., cs2.LogTrain)
cs2.Train.y <- cs2.LogTrain[,2]

cvfit <- cv.glmnet(cs2.Train.x, cs2.Train.y, family = "binomial", type.measure = "class", nlambda = 1000)

plot(cvfit)
coef(cvfit, s = "lambda.min")

# Cv Missclassification
print("Cv Error Rate:")
cvfit$cvm[which(cvfit$lambda==cvfit$lambda.min)]


# Optimal Penalty
print("Penalty Value:")
cvfit$lambda.min

# Final Model
finalmodel <- glmnet(cs2.Train.x, cs2.Train.y, family = "binomial", lambda = cvfit$lambda.min)

# Get predictions from Lasso Model on Test set
cs2.Test.x <- model.matrix(Attrition ~ ., cs2.LogTest)

fit.pred.lasso <- predict(finalmodel, newx = cs2.Test.x, type = "response")

p = data.frame(Att = cs2.LogTest$Attrition, Preds = fit.pred.lasso)
names(p)[2] <- 'Preds'
p %>% group_by(Att, Preds) %>% ggplot(aes(x = Preds, fill = Att)) + geom_boxplot() + facet_grid(rows = vars(p$Att))

# Set cutoff for yes/no
cutoff.lasso = 0.5

class.lasso <- factor(ifelse(fit.pred.lasso > cutoff.lasso, 'Yes','No'),levels = c('No','Yes'))

# How did it do?
print("Confusion Lasso")
confusionMatrix(class.lasso, cs2.LogTest$Attrition)
```
# Custom Model - used to build up complexity -  no significant interactions were found
```{r}
# Custom Log - The best 16 by vizualization - now to pare it down
custom.log <- glm(Attrition ~ Age + DistanceFromHome + YearsWithCurrManager + TotalWorkingYears + YearsInCurrentRole + YearsAtCompany + MonthlyIncome + 
                    JobInvolvement + EducationField + EnvironmentSatisfaction + JobLevel + JobRole + MaritalStatus + OverTime + StockOptionLevel + 
                    WorkLifeBalance, family = "binomial", data = cs2.LogTrain)
summary(custom.log)

# Predictions
fit.pred.custom <- predict(custom.log, newdata = cs2.LogTest, type = "response")

p = data.frame(Att = cs2.LogTest$Attrition, Preds = fit.pred.custom)
names(p)[2] <- 'Preds'
p %>% group_by(Att, Preds) %>% ggplot(aes(x = Preds, fill = Att)) + geom_boxplot() + facet_grid(rows = vars(p$Att))

cutoff.custom = 0.51

class.custom <- factor(ifelse(fit.pred.custom > cutoff.custom, 'Yes','No'),levels = c('No','Yes'))

print("Confusion Custom")
confusionMatrix(class.custom, cs2.LogTest$Attrition)
```
# Used to find the top 3!
```{r}
# Top 3 Finder!
Top3.log <- glm(Attrition ~ JobRole + MaritalStatus + OverTime,
                family = "binomial",
                data = cs2.LogTrain)

summary(Top3.log)

# Predictions
fit.pred.Top3 <- predict(Top3.log, newdata = cs2.LogTest, type = "response")

p = data.frame(Att = cs2.LogTest$Attrition, Preds = fit.pred.Top3)
names(p)[2] <- 'Preds'
p %>% group_by(Att, Preds) %>% ggplot(aes(x = Preds, fill = Att)) + geom_boxplot() + facet_grid(rows = vars(p$Att))

# How'd it do?
cutoff.Top3 <- 0.5385

class.Top3 <- factor(ifelse(fit.pred.Top3 > cutoff.Top3, 'Yes','No'),levels = c('No','Yes'))
confusionMatrix(class.Top3, cs2.LogTest$Attrition)
```
# Iterates the cutoff from 0.0005 to 1 in increments of 0.0005 to find the best
```{r}
# Cut off Finder - Just replace fit.pred.x - with whatever model you want to analyze, first line of the for loop
CM.Acc <- c()
CM.Sens <- c()
CM.Spec <- c()
index <- 1:2000/2000
for (i in index){
  
  class.simple <- factor(ifelse(fit.pred.Top3 > i, 'Yes','No'),levels = c('No','Yes'))
  CM = confusionMatrix(class.simple, cs2.LogTest$Attrition)
 
  CM.Acc <- c(CM.Acc,(CM$table[1,2] + CM$table[2,1])/sum(CM$table))
  CM.Sens <- c(CM.Sens,CM$table[2,1]/(CM$table[2,1] + CM$table[1,1]))
  CM.Spec <- c(CM.Spec,CM$table[1,2]/(CM$table[1,2] + CM$table[2,2]))
}

plot(index,CM.Acc,type="l",col="black",ylab="Percent",xlab="Threshold for predicting Yes",ylim=c(0,1),lwd=2,main = "Top3 Cutoff")
lines(index,CM.Sens,lty=3,col="orange",lwd=2)
lines(index,CM.Spec,lty=5,col="blue",lwd=2)
abline(v = .615, col = "darkorchid4")
legend("top",legend=c("ME","FP","FN"),col=c("black","orange","blue"),lty=1,lwd=1)

```
# A place to see all the confusion matrices and cutoffs
```{r}
# Confusion Matrices!
cutoff.custom <- 0.51
cutoff.lasso <- 0.5
cutoff.step <- 0.41
cutoff.Top3 <- 0.615


class.custom <- factor(ifelse(fit.pred.custom > cutoff.custom, 'Yes','No'),levels = c('No','Yes'))
class.lasso <- factor(ifelse(fit.pred.lasso > cutoff.lasso, 'Yes','No'),levels = c('No','Yes'))
class.step <- factor(ifelse(fit.pred.step > cutoff.step, "Yes", "No"), levels = c("No", "Yes"))
class.Top3 <- factor(ifelse(fit.pred.Top3 > cutoff.Top3, 'Yes','No'),levels = c('No','Yes'))

print("Confusion Lasso")
confusionMatrix(class.lasso, cs2.LogTest$Attrition)

cat("**********************************************\n**********************************************\n\n")

print("Confusion Step")
confusionMatrix(class.step, cs2.LogTest$Attrition)

cat("**********************************************\n**********************************************\n\n")

print("Confusion Custom")
confusionMatrix(class.custom, cs2.LogTest$Attrition)

cat("**********************************************\n**********************************************\n\n")

print("Confusion Top3")
confusionMatrix(class.Top3, cs2.LogTest$Attrition)

```
# ROC Curves to compare results - 
```{r}
# ROC Curves - since we are looking at the negative class (the Yes's of Attrition) we will be looking at the True and False Negative Rates
results.lasso <- prediction(fit.pred.lasso, cs2.LogTest$Attrition, label.ordering = c("No", "Yes"))
roc.lasso <- performance(results.lasso, measure = "tnr", x.measure = "fnr")

results.step <- prediction(fit.pred.step, cs2.LogTest$Attrition, label.ordering = c("No", "Yes"))
roc.step <- performance(results.step, measure = "tnr", x.measure = "fnr")

results.custom <- prediction(fit.pred.custom, cs2.LogTest$Attrition, label.ordering = c("No", "Yes"))
roc.custom <- performance(results.custom, measure = "tnr", x.measure = "fnr")

results.Top3 <- prediction(fit.pred.Top3, cs2.LogTest$Attrition, label.ordering = c("No", "Yes"))
roc.Top3 <- performance(results.Top3, measure = "tnr", x.measure = "fnr")

plot(roc.lasso, col = "red", main = "Comparison of Log Models")
plot(roc.step, col = "blue", add = TRUE)
plot(roc.custom, col = "green", add = TRUE)
plot(roc.Top3, col = "darkorchid4", add = TRUE)
abline(a = 0, b = 1)
legend("bottomright",legend=c("Lasso","Stepwise","Custom", "Top3"),col=c("red","blue","green", "darkorchid4"),lty=1,lwd=1)
```
# KNN Models
```{r}
results.Knn <- prediction(prob, cs2.KNNTest$AttNum,)
roc.Knn <- performance(results.Knn, measure = "tnr", x.measure = "fnr")

# a look at KNN vs the top LogReg Model -  KNN didnt do too well at classifying here due to a lot of the variation coming from the categorical variables
plot(roc.Top3, col = "darkorchid4", main = "Comparison Between Winning Log Model and KNN")
plot(roc.Knn, col = "orange", add = TRUE)
abline(a = 0, b = 1)
legend("bottomright",legend=c("Top3", "Knn"),col=c("darkorchid4", "orange"),lty=1,lwd=1)
```
# Predicitions Out for Classification
```{r}
cs2.NewClass <- read.csv(file = "F:/R For Real/DDS-Case-Study-2/CaseStudy2CompSet No Attrition.csv")
NewClass <- predict(Top3.log, newdata = cs2.NewClass, type = "response")
class.New <- factor(ifelse(NewClass > cutoff.Top3, 'Yes','No'),levels = c('No','Yes'))
report.out <- data.frame(cs2.NewClass[1], class.New)
names(report.out)[2] <- "Predicted Attrition"
write.csv(report.out, file = "F:/R For Real/DDS-Case-Study-2/Case2PredictionsCanton Attrition.csv", row.names = FALSE)

```











