---
title: "Monthly Income"
author: "Adam Canton"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(naniar)
library(GGally)
library(e1071)
library(class)
library(caret)
library(MASS)
library(caret)
library(ggcorrplot)
library(Lahman)
library(olsrr)
library(glmnet)
library(cowplot)
library(gridExtra)
library(car)
library(matrixStats)
library(reshape2)
```

# Intialize
```{r}
# Get data
cs2.data <- read.csv(file = "F:/R For Real/DDS-Case-Study-2/CaseStudy2-data.csv", sep = ",", header = TRUE)

exclude_factors = c("EmployeeCount",'Over18','StandardHours')
cs2.data = cs2.data %>% dplyr::select(-all_of(exclude_factors))

# Split data into sets of different data types 
cs2.data <- cs2.data %>% mutate(AttNum = ifelse(Attrition == "No",0,1))

# Numeric Variables only - and numeric analog to response
cs2.numeric = cs2.data %>% dplyr::select(Age, DailyRate, DistanceFromHome, HourlyRate, MonthlyIncome, MonthlyRate, NumCompaniesWorked, PercentSalaryHike,
                                  TotalWorkingYears, TrainingTimesLastYear, YearsAtCompany, YearsInCurrentRole, YearsSinceLastPromotion,
                                  YearsWithCurrManager,AttNum)
```


# Correlations of continous variables -  none high enough to want to get rid of them
```{r}
corr <- round(cor(cs2.numeric), 3)

ggcorrplot(corr, hc.order = TRUE, type = "lower",
           lab = TRUE, lab_size = 3, method = "circle",
           colors = c("tomato2", "white", "springgreen3"),
           title = "Correlations of Selected Variables",
           ggtheme = theme_bw())

```
# Lots of Graphs of categorical variables vs Monthly Income - Interesting ones were pulled out in the block below
```{r}
g1 = cs2.data %>% ggplot(aes(x = Education, y =  MonthlyIncome, group = Education)) + geom_boxplot()


g2 = cs2.data %>% ggplot(aes(x = EducationField, y = MonthlyIncome)) + geom_boxplot()


g3 = cs2.data %>% ggplot(aes(x = BusinessTravel, y = MonthlyIncome)) + geom_boxplot()


g4 = cs2.data %>% ggplot(aes(x = Gender, y = MonthlyIncome)) + geom_boxplot()


g5 = cs2.data %>% ggplot(aes(x = Department, y = MonthlyIncome)) + geom_boxplot()


g6 = cs2.data %>% ggplot(aes(x = EnvironmentSatisfaction, y = MonthlyIncome, group = EnvironmentSatisfaction)) + geom_boxplot()


g7 = cs2.data %>% ggplot(aes(x = JobInvolvement, y = MonthlyIncome, group = JobInvolvement)) + geom_boxplot()


g8 = cs2.data %>% ggplot(aes(x = JobLevel, y = MonthlyIncome, group = JobLevel)) + geom_boxplot() + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

g9 = cs2.data %>% ggplot(aes(x = JobRole, y = MonthlyIncome)) + geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1)) + theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

g10 = cs2.data %>% ggplot(aes(x = JobSatisfaction, y = MonthlyIncome, group = JobSatisfaction)) + geom_boxplot()


g11 = cs2.data %>% ggplot(aes(x = MaritalStatus, y = MonthlyIncome)) + geom_boxplot()


g12 = cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = MonthlyIncome, group = NumCompaniesWorked)) + geom_boxplot()


g13 = cs2.data %>% ggplot(aes(x = OverTime, y = MonthlyIncome)) + geom_boxplot()


g14 = cs2.data %>% ggplot(aes(x = PerformanceRating, y = MonthlyIncome, group = PerformanceRating)) + geom_boxplot()


g15 = cs2.data %>% ggplot(aes(x = RelationshipSatisfaction, y = MonthlyIncome, group = RelationshipSatisfaction)) + geom_boxplot()


g16 = cs2.data %>% ggplot(aes(x = StockOptionLevel, y = MonthlyIncome, group = StockOptionLevel)) + geom_boxplot()


g17 = cs2.data %>% ggplot(aes(x = TrainingTimesLastYear, y = MonthlyIncome, group = TrainingTimesLastYear)) + geom_boxplot()


g18 = cs2.data %>% ggplot(aes(x = WorkLifeBalance, y = MonthlyIncome, group = WorkLifeBalance)) + geom_boxplot()


# Gather graphs in a plot grid
plot_grid(g3, g4, g6,g7,g10, g11, nrow = 2, ncol = 3)

plot_grid(g13, g14, g15,g16, g17,g18, nrow = 2, ncol = 3)
```

# The ones that showed differences
```{r}
# Interesting
g1
g2
g5
g8
g9
g12
```

# The Continous Variables vs Monthly Income - 
```{r}
cs2.data %>% ggplot(aes(x = MonthlyRate, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = MonthlyIncome, color = Attrition)) + geom_point()

# clearly a strong relationship here
cs2.data %>% ggplot(aes(x = TotalWorkingYears, y = MonthlyIncome, color = Attrition)) + geom_point()

# not as related as expected -  though clear positive relationship
cs2.data %>% ggplot(aes(x = YearsAtCompany, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsInCurrentRole, y =  MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsSinceLastPromotion, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsWithCurrManager, y = MonthlyIncome, color = Attrition)) + geom_point()

```


# Set Training and Test
```{r}
# Set training and test sets 70/30
set.seed(35)
index <- sample(1:dim(cs2.data)[1],floor(0.7*dim(cs2.data)),replace=F)
train.mi <- cs2.data[index,]
test.mi <- cs2.data[-index,]

```

# Full Model
```{r}
# this has supprisingly good fit stats, weirdly grouped residuals though
Model.FullMI1 <- lm(MonthlyIncome ~ ., data = cs2.data[,-c(1,34)])
vif(Model.FullMI1)
summary(Model.FullMI1)
ols_plot_resid_fit(Model.FullMI1)
ols_plot_resid_lev(Model.FullMI1)
ols_plot_resid_qq(Model.FullMI1)
ols_plot_resid_hist(Model.FullMI1)
ols_plot_cooksd_bar(Model.FullMI1)
```
# Looking for Interactions
```{r}
# enter the variables you want to find interactions between -  keep it brief
cs2.reduced <- cs2.data %>% dplyr::select(JobLevel, JobRole, TotalWorkingYears, MonthlyIncome,StockOptionLevel)

Model.Reduced <- lm(MonthlyIncome ~ (.)^2, data = cs2.reduced )

# a look at how good each set is
ols_step_all_possible(Model.Reduced)
```

```{r}
# Selected by step model
Model.MIStep = lm(MonthlyIncome ~ JobLevel + JobRole + TotalWorkingYears + BusinessTravel + Gender + DailyRate + MonthlyRate + 
                    YearsWithCurrManager + YearsSinceLastPromotion + DistanceFromHome + EmployeeNumber, data = cs2.data[,-34])
vif(Model.MIStep)
summary(Model.MIStep)
ols_plot_resid_fit(Model.MIStep)
ols_plot_resid_lev(Model.MIStep)
ols_plot_resid_qq(Model.MIStep)
ols_plot_resid_hist(Model.MIStep)
ols_plot_cooksd_bar(Model.MIStep)
```

```{r}
# partial residuals of the step model just input the model name you would like to look at.
ols_plot_added_variable(Model.MIMin)
```

```{r}
Model.MIMin <- lm(MonthlyIncome ~ JobRole + JobLevel + TotalWorkingYears + JobLevel*JobRole + JobRole*TotalWorkingYears, data = cs2.data[,-34])
vif(Model.MIMin)
summary(Model.MIMin)
ols_plot_diagnostics(Model.MIMin)
#ols_plot_resid_fit(Model.MIMin)
#ols_plot_resid_lev(Model.MIMin)
#ols_plot_resid_qq(Model.MIMin)
#ols_plot_resid_hist(Model.MIMin)
#ols_plot_cooksd_bar(Model.MIMin)
```

# A place to plug in whatever and give it a run
```{r}
# Crazy Model
Model.MICrazy <- lm(MonthlyIncome ~ JobRole + JobLevel + TotalWorkingYears + Gender + 
                      JobRole*Gender+JobLevel*JobRole + JobRole*TotalWorkingYears,
                    data = cs2.data[,-c(1,34)])

vif(Model.MICrazy)
summary(Model.MICrazy)
ols_plot_resid_fit(Model.MICrazy)
ols_plot_resid_lev(Model.MICrazy)
ols_plot_resid_qq(Model.MICrazy)
ols_plot_resid_hist(Model.MICrazy)
ols_plot_cooksd_bar(Model.MICrazy)
```

# Model Benchmarking -  generally the minimum model the optimal choice
```{r, warning=FALSE}
# Set number of times you would like to repeat the sampling/testing 
iterations = 1:500

rmseStep = c()
rmseFull = c()
rmseMin = c()
rmseCrazy = c()

# Start of Loop
for(i in iterations){
  # Resets sample every iteration 
  #set.seed(i)
  index <- sample(1:dim(cs2.data)[1],floor(0.7*dim(cs2.data)),replace=F)
  train.mi <- cs2.data[index,]
  test.mi <- cs2.data[-index,]
  

  # the model runs 
   
  Model.MIStep = lm(MonthlyIncome ~ JobLevel + JobRole + TotalWorkingYears + BusinessTravel + Gender + DailyRate + MonthlyRate + 
                    YearsWithCurrManager + YearsSinceLastPromotion + DistanceFromHome + EmployeeNumber, data = train.mi[,-c(1,34)])
  
  Model.FullMI1 <- lm(MonthlyIncome ~ ., data = train.mi[,-c(1,34)])
  
  Model.MIMin <- lm(MonthlyIncome ~ JobRole + JobLevel + TotalWorkingYears + 
                      JobLevel*JobRole + JobRole*TotalWorkingYears + JobLevel*TotalWorkingYears, data = train.mi[,-c(1,34)])
  
  Model.MICrazy <- lm(MonthlyIncome ~ JobRole + JobLevel + TotalWorkingYears + Gender + 
                      JobRole*Gender+JobLevel*JobRole + JobRole*TotalWorkingYears,data = train.mi[,-c(1,34)])
  
  # predictors and column building
  # Model 1 - Step
  predictions1 <- Model.MIStep %>% predict(test.mi)
  
  d1 = data.frame(R2 = R2(predictions1,test.mi$MonthlyIncome),
                  RMSE = RMSE(predictions1,test.mi$MonthlyIncome), MAE = MAE(predictions1, test.mi$MonthlyIncome))
  rmseStep = c(rmseStep,d1$RMSE)
  
  # Model 2 - Full
  predictions2 <- Model.FullMI1 %>% predict(test.mi)

    d2 = data.frame(R2 = R2(predictions2,test.mi$MonthlyIncome),
                RMSE = RMSE(predictions2,test.mi$MonthlyIncome), MAE = MAE(predictions2, test.mi$MonthlyIncome))
  rmseFull = c(rmseFull, d2$RMSE)
  
  # Model 3 - MIN 
  predictions3 <- Model.MIMin %>% predict(test.mi)
  
  d3= data.frame(R2 = R2(predictions3,test.mi$MonthlyIncome),
                RMSE = RMSE(predictions3,test.mi$MonthlyIncome), MAE = MAE(predictions3, test.mi$MonthlyIncome))
  rmseMin = c(rmseMin, d3$RMSE)
  
  # Model 4 - Crazy 
  predictions4 <- Model.MICrazy %>% predict(test.mi)
  
  d4= data.frame(R2 = R2(predictions4,test.mi$MonthlyIncome),
                RMSE = RMSE(predictions4,test.mi$MonthlyIncome), MAE = MAE(predictions4, test.mi$MonthlyIncome))
  rmseCrazy = c(rmseCrazy, d4$RMSE)
  
  
} # End for
# putting the dataframe together and outputting relevant statistics
Model.Average.RMSE = cbind(rmseStep, rmseFull, rmseMin, rmseCrazy)
rmsedf = as.data.frame(Model.Average.RMSE)
Means = colMeans(Model.Average.RMSE)
SDs = round(colSds(Model.Average.RMSE), 3)
range1 = max(rmsedf$rmseStep) - min(rmsedf$rmseStep)
range2 = max(rmsedf$rmseFull) - min(rmsedf$rmseFull)
range3 = max(rmsedf$rmseMin) - min(rmsedf$rmseMin)
range4 = max(rmsedf$rmseCrazy) - min(rmsedf$rmseCrazy)
rmsedf1 = melt(rmsedf,rmse = c("n", "rmse"))

# Looking at descriptive stats
Means
print("Standard Devs")
SDs
print("ranges - measure of variance between train/test shuffles")
print(paste("Model Step Range" , round(range1, 3)))
print(paste("Model Full Range" , round(range2, 3)))
print(paste("Model Min Range" , round(range3, 3)))
print(paste("Model Crazy Range" , round(range3, 3)))
cat("Summary: 
    ")
summary(Model.Average.RMSE)

# Scatter
Pred1 <- data.frame(Value = predictions1, Model = "Step")
Pred2 <- data.frame(Value = predictions2, Model = "Full")
Pred3 <- data.frame(Value = predictions3, Model = "Min")
Pred4 <- data.frame(Value = predictions4, Model = "Crazy")
PredActual <- data.frame(ActualValue = test.mi$MonthlyIncome)
PredAll <- rbind(Pred1, Pred2, Pred3, Pred4)
PredActual <- rbind(PredActual,PredActual, PredActual, PredActual)
PredAll <- cbind(PredAll, PredActual)
PredAll %>% ggplot(aes(x = Value, y = ActualValue, fill = Model)) + geom_point(aes(color = Model)) + geom_smooth(method = "lm")+
  facet_wrap(facets = PredAll$Model) + ggtitle("Scatter Plot of Models") + xlab("Predicted") + ylab("Observed")

# Column
rmsedf1 %>% group_by(variable) %>% summarise(mean = (mean(value))) %>% 
  ggplot(aes(x = reorder(variable, -mean), y = mean, fill = variable)) + geom_col(width = 0.75) + geom_text(aes(label = round(mean,3), vjust = -0.5)) + 
  ggtitle(sprintf("Average RMSE over %s Shuffles (Linear Models)", max(iterations))) + xlab("Model #") + ylab("Mean RMSE")

# Boxplot
f1 = rmsedf1 %>%  ggplot(aes(x = variable, y = value)) + geom_boxplot(aes(fill = variable)) + facet_wrap(~variable,ncol = TRUE) +
  ggtitle("Mean RMSE Distribution by Model") + ylab("Mean RMSE") + coord_flip() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())
# Histogram
f2 = rmsedf1 %>%  ggplot(aes(x = value)) + geom_histogram(aes(fill = variable)) + facet_wrap(~variable,ncol = TRUE) +
  ggtitle("Mean RMSE Distribution by Model") + xlab("Mean RMSE") + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())

f1
f2
# Here we can see there is no significant difference between the models in terms of RMSE
t.test(rmseStep,rmseFull, paired = TRUE, conf.level = 0.99)
t.test(rmseMin,rmseFull, paired = TRUE, conf.level = 0.99)
t.test(rmseStep,rmseMin, paired = TRUE, conf.level = 0.99)
t.test(rmseCrazy,rmseMin, paired = TRUE, conf.level = 0.99)
```
# Predictions for new data
```{r}
cs2.NewData <- read.csv(file = "F:/R For Real/DDS-Case-Study-2/CaseStudy2CompSet No Salary.csv")
New.MI <- predict(Model.MIMin,cs2.NewData)
report.out <- data.frame(cs2.NewData[1],New.MI)
names(report.out)[1] <- "ID"
names(report.out)[2] <- "Predicted Monthly Income"
write.csv(report.out, file = "F:/R For Real/DDS-Case-Study-2/Case2PredictionsCanton Salary.csv", row.names = FALSE)
```

