---
title: "EDA1"
author: "Adam Canton"
date: "7/24/2020"
output: html_document
---
# Intialize
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(naniar)
library(GGally)
library(e1071)
library(class)
library(caret)
library(MASS)
library(caret)
library(ggcorrplot)
library(Lahman)
library(olsrr)
library(glmnet)
library(cowplot)
```

```{r}
# Get data
cs2.data <- read.csv(file = "F:/R For Real/DDS-Case-Study-2/CaseStudy2-data.csv", sep = ",", header = TRUE)

exclude_factors = c("EmployeeCount",'Over18','StandardHours')
cs2.data = cs2.data %>% dplyr::select(-all_of(exclude_factors))

# Split data into sets of different data types 
cs2.data <- cs2.data %>% mutate(AttNum = ifelse(Attrition == "No",0,1))
cs2.numeric = cs2.data %>% dplyr::select(Age, DailyRate, DistanceFromHome, HourlyRate, MonthlyIncome, MonthlyRate, NumCompaniesWorked, PercentSalaryHike,
                                  TotalWorkingYears, TrainingTimesLastYear, YearsAtCompany, YearsInCurrentRole, YearsSinceLastPromotion,
                                  YearsWithCurrManager,AttNum)

```

```{r}
# No Apparent NA Values, need to check for other NA identifiers
gg_miss_var(cs2.data)

na_count <- sapply(cs2.data, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```

```{r}
str(cs2.data)
summary(cs2.data)
```

```{r}
# take a look at collinearity
pairs(cs2.numeric)
```


# Correlations of numeric variables and Numeric analog of response
```{r}
# Nothing looks so highly correlated that we should want to get rid of it. 

corr <- round(cor(cs2.numeric), 3)

ggcorrplot(corr, hc.order = TRUE, type = "lower",
           lab = TRUE, lab_size = 3, method = "square",
           colors = c("tomato2", "white", "springgreen3"),
           title = "Correlations of Selected Continous Variables")
```

# Age Vs Everything (numeric)
```{r}
# Adding in the response

# Attrition Occurs younger invariate of rate
cs2.data %>% ggplot(aes(x = Age, y = DailyRate, color = Attrition)) + geom_point()

# Seems Most workers lives within 10 miles - needs some follow up what percentages - Distance from home invariate with age
cs2.data %>% ggplot(aes(x = Age, y = DistanceFromHome, color = Attrition)) + geom_point()

# Attrition seems to occur younger no matter the rate
cs2.data %>% ggplot(aes(x = Age, y = HourlyRate, color = Attrition)) + geom_point()

# Possible further investigation
cs2.data %>% ggplot(aes(x = Age, y = MonthlyIncome, color = Attrition)) + geom_point()

# Eh
cs2.data %>% ggplot(aes(x = Age, y = MonthlyRate, color = Attrition)) + geom_point()

# Further Investigation
cs2.data %>% ggplot(aes(x = Age, y = NumCompaniesWorked, color = Attrition)) + geom_point()

# Further Investigation
cs2.data %>% ggplot(aes(x = Age, y = PercentSalaryHike, color = Attrition)) + geom_point()

# Further Investigation - 
cs2.data %>% ggplot(aes(x = Age, y = TotalWorkingYears, color = Attrition)) + geom_point()

# eh
cs2.data %>% ggplot(aes(x = Age, y = TrainingTimesLastYear, color = Attrition)) + geom_point()

# eh
cs2.data %>% ggplot(aes(x = Age, y = YearsAtCompany, color = Attrition)) + geom_point()

# 
cs2.data %>% ggplot(aes(x = Age, y = YearsInCurrentRole, color = Attrition)) + geom_point()
cs2.data %>% ggplot(aes(x = Age, y = YearsSinceLastPromotion, color = Attrition)) + geom_point()

# pretty interesting here how zero line is quite telling looks like a majority of attrition happens within 1 year with a manager
cs2.data %>% ggplot(aes(x = Age, y = YearsWithCurrManager, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsWithCurrManager, fill = Attrition)) + geom_histogram(binwidth = 1) + 
  aes(y = stat(count)/sum(stat(count))) + scale_y_continuous(labels = scales::percent) + facet_wrap(~Attrition)
```



# Stuff vs Daily Rate
```{r}
cs2.data %>% ggplot(aes(x = DailyRate, y = DistanceFromHome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = HourlyRate, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = MonthlyRate, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = NumCompaniesWorked, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = PercentSalaryHike, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = TotalWorkingYears, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = TrainingTimesLastYear, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = YearsAtCompany, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = YearsSinceLastPromotion, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DailyRate, y = YearsWithCurrManager, color = Attrition)) + geom_point()

```


# Stuff vs Disatnce from home
```{r}
cs2.data %>% ggplot(aes(x = DistanceFromHome, y = HourlyRate , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = MonthlyIncome , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = MonthlyRate , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = NumCompaniesWorked , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = PercentSalaryHike, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = TotalWorkingYears, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = TrainingTimesLastYear, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = YearsAtCompany, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = YearsSinceLastPromotion, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = DistanceFromHome, y = YearsWithCurrManager, color = Attrition)) + geom_point()

```
# Stuff vs Hourly Rate
```{r}
cs2.data %>% ggplot(aes(x = HourlyRate, y = MonthlyIncome, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = MonthlyRate  , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = NumCompaniesWorked , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = PercentSalaryHike , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = TotalWorkingYears , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = HourlyRate, y = YearsWithCurrManager , color = Attrition)) + geom_point()

```


# Stuff vs Monthly Income
```{r}
cs2.data %>% ggplot(aes(x = MonthlyIncome, y = MonthlyRate  , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = NumCompaniesWorked , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = PercentSalaryHike , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = TotalWorkingYears , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyIncome, y = YearsWithCurrManager , color = Attrition)) + geom_point()

```


# Monthly Rate
```{r}
cs2.data %>% ggplot(aes(x = MonthlyRate, y = NumCompaniesWorked , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = PercentSalaryHike , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = TotalWorkingYears , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = MonthlyRate, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# NumCompaniesWorked
```{r}
cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = PercentSalaryHike , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = TotalWorkingYears , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = NumCompaniesWorked, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# Percent salary hike
```{r}
cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = TotalWorkingYears , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = PercentSalaryHike, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# TotalWorkingYears
```{r}
cs2.data %>% ggplot(aes(x = TotalWorkingYears, y = TrainingTimesLastYear , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TotalWorkingYears, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TotalWorkingYears, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TotalWorkingYears, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TotalWorkingYears, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# Training Times Last Year
```{r}
cs2.data %>% ggplot(aes(x = TrainingTimesLastYear, y = YearsAtCompany , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TrainingTimesLastYear, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TrainingTimesLastYear, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = TrainingTimesLastYear, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# Years at Company
```{r}
# Years positively correlated with other time measuring variable no suprise
cs2.data %>% ggplot(aes(x = YearsAtCompany, y =  YearsInCurrentRole, color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsAtCompany, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsAtCompany, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# Years In Current Role
```{r}
cs2.data %>% ggplot(aes(x = YearsInCurrentRole, y = YearsSinceLastPromotion , color = Attrition)) + geom_point()

cs2.data %>% ggplot(aes(x = YearsInCurrentRole, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```


# Years Since Last Promotion
```{r}
cs2.data %>% ggplot(aes(x = YearsSinceLastPromotion, y = YearsWithCurrManager , color = Attrition)) + geom_point()
```

# The Well Plotted Interesting Stuff
## Something interesting 1 -  Cumulative Attrition by Years with current manager
```{r, warning = FALSE}
cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsWithCurrManager)) + geom_histogram(binwidth = 1, fill = "#00BFC4") + 
  aes(y = stat(count)/sum(stat(count))) + scale_y_continuous(labels = scales::percent) + ylab("Percent Attrition") + xlab("Years With Current Manager") + 
  ggtitle("Distribution of Attrition by Years with Current Manager") + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") + 
  scale_x_continuous(breaks = sort(c(seq(0,20,5), 3)), limits = c(0,20), expand = c(0,0))

# Of those who leave 40% do so before the end of the first year, 60% by year 3, and by year 7 90%
cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsWithCurrManager)) + stat_ecdf() + 
  scale_y_continuous(breaks = seq(0,1,0.1)) + scale_x_continuous(breaks = seq(1,15,1)) + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") +
  geom_vline(xintercept = 7, color = "darkred", size = 1.5, linetype = "dashed") +
  ggtitle("Cumulative Proportion of Attrition by Years with Current Manager") + ylab("Cumulative Proportion of Attrition") +
  xlab("Years With Current Manager")


cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsInCurrentRole)) + geom_histogram(binwidth = 1, fill = "#00BFC4") + 
  aes(y = stat(count)/sum(stat(count))) + scale_y_continuous(labels = scales::percent) + ylab("Percent Attrition") + xlab("Years in Current Role") + 
  ggtitle("Distribution of Attrition by Years in Current Role") + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") + 
  scale_x_continuous(breaks = sort(c(seq(0,20,5), 3)), limits = c(0,20), expand = c(0,0))

# Of those who leave 40% do so before the end of the first year, 60% by year 3, and by year 7 90%
cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsInCurrentRole)) + stat_ecdf() + 
  scale_y_continuous(breaks = seq(0,1,0.1)) + scale_x_continuous(breaks = seq(1,15,1)) + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") +
  geom_vline(xintercept = 7, color = "darkred", size = 1.5, linetype = "dashed") +
  ggtitle("Cumulative Proportion of Attrition by Years In Current Role") + ylab("Cumulative Proportion of Attrition") +
  xlab("Years In Current Role")


cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsAtCompany)) + geom_histogram(binwidth = 1, fill = "#00BFC4") + 
  aes(y = stat(count)/sum(stat(count))) + scale_y_continuous(labels = scales::percent) + ylab("Percent Attrition") + xlab("Years at Company") + 
  ggtitle("Distribution of Attrition by Years at Company") + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") + 
  scale_x_continuous(breaks = sort(c(seq(0,20,5), 3)), limits = c(0,20), expand = c(0,0))

# Of those who leave 40% do so before the end of the first year, 60% by year 3, and by year 7 90%
cs2.data %>% filter(Attrition == "Yes") %>% ggplot(aes(x = YearsAtCompany)) + stat_ecdf() + 
  scale_y_continuous(breaks = seq(0,1,0.1)) + scale_x_continuous(breaks = seq(1,20,1), limits = c(0,20)) + 
  geom_vline(xintercept = 2, color = "red", size = 1.5, linetype = "dashed") +
  geom_vline(xintercept = 10, color = "darkred", size = 1.5, linetype = "dashed") +
  ggtitle("Cumulative Proportion of Attrition by Years At Company") + ylab("Cumulative Proportion of Attrition") +
  xlab("Years At Company")
```
## Jobfullfillment and Marital Status
```{r}
# No change in worklife balance between the groups
g1 = ggplot(cs2.data) +
      aes(x = MaritalStatus, y = WorkLifeBalance, fill = MaritalStatus) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank()) +
      scale_fill_manual(values= c("firebrick1", "darkorchid2", "deepskyblue"))
 
# Single generally make slightly less money than other two, likely age dependent
g2 = ggplot(cs2.data) +
      aes(x = MaritalStatus, y = MonthlyIncome, fill = MaritalStatus) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank()) +
      scale_fill_manual(values= c("firebrick1", "darkorchid2", "deepskyblue"))

# Divorced are reporting lower job satisfactions though their median satisfaction is unchanged
g3 = ggplot(cs2.data) +
      aes(x = MaritalStatus, y = JobSatisfaction, fill = MaritalStatus) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title.x = element_blank()) + 
      scale_fill_manual(values= c("firebrick1", "darkorchid2", "deepskyblue"))
  
g11 = ggdraw() + draw_label("Marital Status and Job Fulfillment", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11,NULL,NULL,NULL,NULL,g1,NULL,g2,NULL,g3, ncol = 5, nrow = 2, rel_widths = c(2,0.5,2,0.5,2), rel_heights = c(0.5,4))
```
## Jobfullfillment and Gender
```{r}
# No change in worklife balance between the groups
g1 = ggplot(cs2.data) +
      aes(x = Gender, y = WorkLifeBalance, fill = Gender) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
      scale_fill_manual(values = c("pink", "dodgerblue1"))
 
# Single generally make slightly less money than other two, likely age dependent
g2 = ggplot(cs2.data) +
      aes(x = Gender, y = MonthlyIncome, fill = Gender) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      scale_fill_manual(values = c("pink", "dodgerblue1"))

# Divorced are reporting lower job satisfactions though their median satisfaction is unchanged
g3 = ggplot(cs2.data) +
      aes(x = Gender, y = JobSatisfaction, fill = Gender) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
      scale_fill_manual(values = c("pink", "dodgerblue1"))
  
g11 = ggdraw() + draw_label("Gender and Job Fulfillment", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11,NULL,NULL,NULL,NULL,g1,NULL,g2,NULL,g3, ncol = 5, nrow = 2, rel_widths = c(2,0.5,2,0.5,2), rel_heights = c(0.5,4))
```

```{r}
# No change in worklife balance between the groups
g1 = ggplot(cs2.data) +
      aes(x = JobLevel, y = WorkLifeBalance, fill = JobLevel, group = JobLevel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 
# Single generally make slightly less money than other two, likely age dependent
g2 = ggplot(cs2.data) +
      aes(x = JobLevel, y = MonthlyIncome, fill = JobLevel, group = JobLevel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Divorced are reporting lower job satisfactions though their median satisfaction is unchanged
g3 = ggplot(cs2.data) +
      aes(x = JobLevel, y = JobSatisfaction, fill = JobLevel, group = JobLevel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
  
g11 = ggdraw() + draw_label("Job Level and Job Fulfillment", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11,NULL,NULL,NULL,NULL,g1,NULL,g2,NULL,g3, ncol = 5, nrow = 2, rel_widths = c(2,0.5,2,0.5,2), rel_heights = c(0.5,4))
```

```{r}
# No change in worklife balance between the groups
g1 = ggplot(cs2.data) +
      aes(x = BusinessTravel, y = WorkLifeBalance, fill = BusinessTravel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
 
# Single generally make slightly less money than other two, likely age dependent
g2 = ggplot(cs2.data) +
      aes(x = BusinessTravel, y = MonthlyIncome, fill = BusinessTravel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Divorced are reporting lower job satisfactions though their median satisfaction is unchanged
g3 = ggplot(cs2.data) +
      aes(x = BusinessTravel, y = JobSatisfaction, fill = BusinessTravel) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
  
g11 = ggdraw() + draw_label("Business Travel and Job Fulfillment", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))


# Yep singles are generally younger...
ggplot(cs2.data) +
      aes(x = MaritalStatus, y = Age, fill = MaritalStatus) +
      geom_boxplot() + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


plot_grid(g11,NULL,NULL,NULL,NULL,g1,NULL,g2,NULL,g3, ncol = 5, nrow = 2, rel_widths = c(2,0.5,2,0.5,2), rel_heights = c(0.5,4))
```

```{r}
# Here we can see that overtime and education field effect attrition. Those who work overtime are much more likely to leave.
# Most severe in marketing -  Human resources seems to have a lot no matter what
cs2.data %>% 
  group_by(OverTime, EducationField, Attrition) %>%
  summarise(count = n()) %>% 
  mutate(Perc = (count/sum(count))) %>%
  ggplot(aes(x = EducationField, y = Perc, fill = Attrition, group = Attrition)) + 
  geom_col() + facet_wrap(~OverTime) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_text(aes(x = EducationField, y = Perc, label = round(Perc,3), group = Attrition), position = position_stack(vjust = 0.5)) +
  ggtitle("Education Field by Overtime and Attrition")

cs2.data %>% 
  group_by(OverTime, JobLevel, Attrition) %>%
  summarise(count = n()) %>% 
  mutate(Perc = (count/sum(count))) %>%
  ggplot(aes(x = JobLevel, y = Perc, fill = Attrition, group = Attrition)) + 
  geom_col() + facet_wrap(~OverTime) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_text(aes(x = JobLevel, y = Perc, label = round(Perc,3), group = Attrition), position = position_stack(vjust = 0.5)) +
  ggtitle("Job Level by Overtime and Attrition")

cs2.data %>% 
  group_by(OverTime, MaritalStatus, Attrition) %>%
  summarise(count = n()) %>% 
  mutate(Perc = (count/sum(count))) %>%
  ggplot(aes(x = MaritalStatus, y = Perc, fill = Attrition, group = Attrition)) + 
  geom_col() + facet_wrap(~OverTime) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_text(aes(x = MaritalStatus, y = Perc, label = round(Perc,3), group = Attrition), position = position_stack(vjust = 0.5)) +
  ggtitle("Marital Status by Overtime and Attrition")

cs2.data %>% 
  group_by(OverTime, JobRole, Attrition) %>%
  summarise(count = n()) %>% 
  mutate(Perc = (count/sum(count))) %>%
  ggplot(aes(x = JobRole, y = Perc, fill = Attrition, group = Attrition)) + 
  geom_col() + facet_wrap(~OverTime) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_text(aes(x = JobRole, y = Perc, label = round(Perc,3), group = Attrition), position = position_stack(vjust = 0.5), size = 2.5) +
  ggtitle("Job Role by Overtime and Attrition")
```


```{r}
#g1 = cs2.data %>% group_by(EmployeeCount) %>% summarise(count = n()) %>% ggplot(aes(x = EmployeeCount, y = count)) + geom_boxplot() + 
      theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.y = element_blank()) + ggtitle("Employee Count is Constant at 870")

#g2 = cs2.data %>% 
      #group_by(Over18) %>% summarise(count = n()) %>% 
      #ggplot(aes(x = Over18, y = count, fill = Over18)) + geom_bar(stat = "identity", width = 0.5) + 
      #theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "none", axis.title.y = element_blank()) +
      #geom_text(aes(label = count), vjust = -0.25) + 
      #ggtitle("All Employees are Over 18") + scale_fill_manual(values = c("steelblue"))

#g11 = ggdraw() + draw_label("No Information Variables", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

#plot_grid(g11, NULL, g1,g2,cols = 2, rows = 2, rel_heights = c(0.25,2))
```

```{r}
cs2.data %>%
  group_by(Attrition) %>%
  summarize(count = n()) %>%
  mutate(Perc = count/sum(count)) %>%
  ggplot(aes(x = Attrition, y = Perc, fill = Attrition)) + geom_col() + 
  geom_text(aes(label = round(Perc,3)), vjust = -0.25) + 
  ggtitle("Attrition Balance in Data set")
```

# Travel
```{r}
ggplot(cs2.data) +
  aes(x = JobRole, y = DistanceFromHome, fill = Attrition) +
  geom_boxplot() +  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7), axis.title.x = element_blank()) +
  ggtitle("Job Role by Distance from Home and Attrition")

ggplot(cs2.data) +
 aes(x = OverTime, y = DistanceFromHome, fill = Attrition) +
 geom_boxplot()


ggplot(cs2.data) +
 aes(x = MaritalStatus, y = DistanceFromHome, fill = Attrition) +
 geom_boxplot()


ggplot(cs2.data) +
 aes(x = BusinessTravel, y = DistanceFromHome, fill = Attrition) +
 geom_boxplot()

```
# Possibly Important Continous Variables
```{r}
g1 = ggplot(cs2.data, aes(x = Attrition, y = YearsWithCurrManager, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank()) + ylab("YrsWManager")

g2 = ggplot(cs2.data, aes(x = Attrition, y = YearsAtCompany, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank()) + ylab("YrsAtCo.")

g3 = ggplot(cs2.data, aes(x = Attrition, y = YearsInCurrentRole, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank()) + ylab("YrsInRole")

g4 = ggplot(cs2.data, aes(x = Attrition, y = Age, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank())

g5 = ggplot(cs2.data, aes(x = Attrition, y = MonthlyIncome, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank())

g6 = ggplot(cs2.data, aes(x = Attrition, y = TotalWorkingYears, fill = Attrition)) + geom_boxplot() + 
      theme(legend.position = "none",axis.title.x = element_blank()) + ylab("WorkingYears")

g7 = ggplot(cs2.data, aes(x = Attrition, y = DistanceFromHome, fill = Attrition)) + geom_boxplot() +
      theme(axis.title.x = element_blank())

g11 = ggdraw() + draw_label("Largest Spread Continous Variables", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11,NULL,NULL,g1,g2,g3,g4,g5,g6,NULL,g7,NULL, rows = 4, cols = 3, rel_heights = c(0.5,2,2,2))
```

```{r}
g1 = cs2.data %>% group_by(JobInvolvement, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = JobInvolvement, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g2 = cs2.data %>% group_by(JobLevel, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = JobLevel, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g3 = cs2.data %>% group_by(JobRole, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = JobRole, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1, size = 8), 
            legend.position = "none", axis.title.y = element_blank())

g4 = cs2.data %>% group_by(MaritalStatus, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = MaritalStatus, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g5 = cs2.data %>% group_by(NumCompaniesWorked, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = NumCompaniesWorked, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g6 = cs2.data %>% group_by(OverTime, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = OverTime, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g7 = cs2.data %>% group_by(StockOptionLevel, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = StockOptionLevel, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g8 = cs2.data %>% group_by(WorkLifeBalance, Attrition) %>% summarise(count = n()) %>% mutate(Perc = (count/sum(count))) %>% 
      ggplot(aes(x = WorkLifeBalance, y = Perc, fill = Attrition)) + geom_bar(stat = "identity") + 
      theme(axis.text.x = element_text(angle = 90, vjust = 0.65, hjust = 1), legend.position = "none", axis.title.y = element_blank())

g11 = ggdraw() + draw_label("Largest Difference Categorical Variables", fontface = 'bold', x = 0, hjust = 0) + theme(plot.margin = margin(0,0,0,7))

plot_grid(g11,NULL,NULL,NULL,g1,g2,g3,g4,NULL,NULL,NULL,NULL,g5,g6,g7,g8, cols = 4, rows = 4, rel_heights = c(0.3,2,0.5,2))
```

